Dynein project log

### 2017-01-28 thesis_stuff/thesis_stuff.tex
Add precision to stepping data printout.
Add few numbers from Weihong's paper to thesis.

\begin{center}
  \begin{tabular}{| l | l | l | l | l | l | l | p{3cm} | p{2cm} | l | p{5cm} |}
    \hline
    Ls & Lt & kb & kub & cm & cb & ct & $\Big<P(\mbox{unbind per dt})\Big>$ & $\Big<\mbox{step time}\Big>$ & run & errors\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.02 & 0.02 & 0.02 & & & & NaN! tail crashes into MT \\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.11 & 0.11 & 0.11 & & & & NaN! motor crashes into MT \\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.18 & 0.18 & 0.18 & & & & NaN! tail crashes into MT \\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.23 & 0.23 & 0.23 & & $3.7e-4$ & & NaN! tail crashes into MT \\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.58 & 0.58 & 0.58 & & $9.1e-4$ & & NaN! motor crashes into MT \\\hline
    22.1 & 11.1 & 5000 & 5000 & 1.16 & 1.16 & 1.16 & $2.7e-13$ & $6.8e-4$ & & \\\hline
    22.1 & 11.1 & 5000 & 5000 & 1.74 & 1.74 & 1.74 & & & & \\\hline
    22.1 & 11.1 & 5000 & 5000 & 2.32 & 2.32 & 2.32 & & & & \\\hline
    22.1 & 11.1 & 5000 & 5000 & 2.90 & 2.90 & 2.90 & $9.5e-32$ & & & \\\hline
    22.1 & 11.1 & 5000 & 5000 & 3.49 & 3.49 & 3.49 & $2.7e-35$ & & & \\\hline
    22.1 & 11.1 & 5000 & 3500 & 1.00 & 1.00 & 1.00 & $2.7e-12$ & $1.7e-3$ & & NaN! motor crashes into MT\\\hline
    22.1 & 11.1 & 5000 & 3500 & 2.32 & 2.32 & 2.32 & $4.1e-18$ & $5.5e-3$ & & \\\hline
    22.1 & 11.1 & 5000 & 2000 & 1.00 & 1.00 & 1.00 & $1.5e-12$ & $2.2e-4$ & & \\\hline
    22.1 & 11.1 & 5000 & 2000 & 2.32 & 2.32 & 2.32 & $2.2e-18$ & & & \\\hline
    22.1 & 11.1 & 5000 & 1000 & 1.00 & 1.00 & 1.00 & & & & \\\hline
    22.1 & 11.1 & 5000 & 1000 & 2.32 & 2.32 & 2.32 & & & & \\\hline
    22.1 & 11.1 & 5000 &  180 & 1.00 & 1.00 & 1.00 & & $1.8^{-2}$ & & \\\hline
    22.1 & 11.1 & 5000 &  180 & 1.30 & 1.30 & 1.30 & & $1.9^{-2}$ & & \\\hline
    22.1 & 11.1 & 5000 &  180 & 1.60 & 1.60 & 1.60 & & $1.9^{-2}$ & & \\\hline
    22.1 & 11.1 & 5000 &  180 & 1.90 & 1.90 & 1.90 & & $1.9^{-2}$ & & \\\hline
    22.1 & 11.1 & 5000 &  180 & 2.10 & 2.10 & 2.10 & & $1.9^{-2}$ & & \\\hline
    22.1 & 11.1 & 5000 &  180 & 2.25 & 2.25 & 2.25 & & $1.9^{-2}$ & & \\\hline
    22.1 & 11.1 & 5000 &  180 & 2.40 & 2.40 & 2.40 & & $1.9^{-2}$ & & \\\hline
    22.1 & 11.1 & 5000 &  180 & 2.55 & 2.55 & 2.55 & & $1.9^{-2}$ & & \\\hline
    22.1 & 11.1 & 5000 &  180 & 2.70 & 2.70 & 2.70 & & $1.9^{-2}$ & & \\\hline
    22.1 & 11.1 & 5000 &  180 & 3.10 & 3.10 & 3.10 & & $1.9^{-2}$ & & \\\hline
  \end{tabular}
  \textbf{New possibly right angle scheme run data}
\end{center}

@@

@@

Has the stepping histograms we are trying to reproduce computationally.

>>>>

\begin{center}
  \begin{tabular}{| l | l | l | l | l | l | l | p{3cm} | p{2cm} | l | p{5cm} |}
    \hline
    Ls & Lt & kb & kub & cm & cb & ct & $\Big<P(\mbox{unbind per dt})\Big>$ & $\Big<\mbox{step time}\Big>$ & run & errors\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.02 & 0.02 & 0.02 & & & & NaN! tail crashes into MT \\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.11 & 0.11 & 0.11 & & & & NaN! motor crashes into MT \\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.18 & 0.18 & 0.18 & & & & NaN! tail crashes into MT \\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.23 & 0.23 & 0.23 & & $3.7e-4$ & & NaN! tail crashes into MT \\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.58 & 0.58 & 0.58 & & $9.1e-4$ & & NaN! motor crashes into MT \\\hline
    22.1 & 11.1 & 5000 & 5000 & 1.16 & 1.16 & 1.16 & $2.7e-13$ & $6.8e-4$ & & \\\hline
    22.1 & 11.1 & 5000 & 5000 & 1.74 & 1.74 & 1.74 & & & & \\\hline
    22.1 & 11.1 & 5000 & 5000 & 2.32 & 2.32 & 2.32 & & & & \\\hline
    22.1 & 11.1 & 5000 & 5000 & 2.90 & 2.90 & 2.90 & $9.5e-32$ & & & \\\hline
    22.1 & 11.1 & 5000 & 5000 & 3.49 & 3.49 & 3.49 & $2.7e-35$ & & & \\\hline
    22.1 & 11.1 & 5000 & 3500 & 1.00 & 1.00 & 1.00 & $2.7e-12$ & $1.7e-3$ & & NaN! motor crashes into MT\\\hline
    22.1 & 11.1 & 5000 & 3500 & 2.32 & 2.32 & 2.32 & $4.1e-18$ & $5.5e-3$ & & \\\hline
    22.1 & 11.1 & 5000 & 2000 & 1.00 & 1.00 & 1.00 & $1.5e-12$ & $2.2e-4$ & & \\\hline
    22.1 & 11.1 & 5000 & 2000 & 2.32 & 2.32 & 2.32 & $2.2e-18$ & & & \\\hline
    22.1 & 11.1 & 5000 & 1000 & 1.00 & 1.00 & 1.00 & & & & \\\hline
    22.1 & 11.1 & 5000 & 1000 & 2.32 & 2.32 & 2.32 & & & & \\\hline
    %% 22.1 & 11.1 & 5000 &  180 & 1.00 & 1.00 & 1.00 & & $1.8^{-2}$ & & \\\hline
    %% 22.1 & 11.1 & 5000 &  180 & 1.30 & 1.30 & 1.30 & & $1.9^{-2}$ & & \\\hline
    %% 22.1 & 11.1 & 5000 &  180 & 1.60 & 1.60 & 1.60 & & $1.9^{-2}$ & & \\\hline
    %% 22.1 & 11.1 & 5000 &  180 & 1.90 & 1.90 & 1.90 & & $1.9^{-2}$ & & \\\hline
    %% 22.1 & 11.1 & 5000 &  180 & 2.10 & 2.10 & 2.10 & & $1.9^{-2}$ & & \\\hline
    22.1 & 11.1 & 5000 &  180 & 2.25 & 2.25 & 2.25 & & $1.9^{-2}$ & & \\\hline
    %% 22.1 & 11.1 & 5000 &  180 & 2.40 & 2.40 & 2.40 & & $1.9^{-2}$ & & \\\hline
    %% 22.1 & 11.1 & 5000 &  180 & 2.55 & 2.55 & 2.55 & & $1.9^{-2}$ & & \\\hline
    %% 22.1 & 11.1 & 5000 &  180 & 2.70 & 2.70 & 2.70 & & $1.9^{-2}$ & & \\\hline
    %% 22.1 & 11.1 & 5000 &  180 & 3.10 & 3.10 & 3.10 & & $1.9^{-2}$ & & \\\hline
    22.1 & 11.1 & 300 &  180 & 2.40 & 2.40 & 2.40 & & $1.9^{-2}$ & & \\\hline
    22.1 & 11.1 & 100 &  180 & 2.40 & 2.40 & 2.40 & & $1.9^{-2}$ & & \\\hline
  \end{tabular}
  \textbf{New possibly right angle scheme run data}
\end{center}

@@

\subsection{A Simple Theoretical Model Explains Dynein’s Response to Load}
Yi Qin Gao 2006

Two reaction coordinates. First is where it is in the ATP, ADP-Pi, ADP, Apo cycle. Second is domain orientation and MT binding status position.\\

Stalling force increases by 4-fold when [ATP] goes from 0.1 to 1mM, a much more dramatic change than seen in kinesin. (they cite this claim). Dynein's step size also varies a lot with load -- we could easily test if our model behaves this way, as well.\\

ATP binding rate to apo dynein: $7*1-^5/m/s$

This seems like a good paper to finish eventually. It would be something to compare our results to.\\

@@

Has the stepping histograms we are trying to reproduce computationally.\\

Velocities reported here are probably bad, but the step lengths are good. Step length not influenced by [ATP].\\

At Weihong's 1mM [ATP], the stepping rate for their dynein is $k = 1.78 ± 0.13 s−1$. Thus dynein takes a step roughly every $0.58s$ when in low-ATP conditions. Average velocity at this concentration si $134 ± 60.4 nm s−1$. Run length of $1.06 ± 0.044 µm$.\\

Seems to be a difference between different types of steps: tail steps are a single motion of the tail, and Weihong says are about 10nm (2d). Motions of each motor are 14-16nm. 77\% are forward steps.\\

It's potentially important to note the dynein species used, though probably not since Weihong didn't mention it much in the paper.\\
